Title

### 2024-08-30 paper.tex
fix pronouns???  i think they're better now

\begin{corollary}\label{bs_iso}
    \begin{align*}
        B_{I, (\rho_i)} \cong & \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
        & \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
    \end{align*}
\end{corollary}
\begin{proof}
    Here I use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} says that this is an isomorphism.
\end{proof}

@@

\par I claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).

@@

        \par I claim that \(f_n \in W\) as well.
        To see this, we consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).

@@

\subsection{A `normalization' fact about Jordan bases}
\begin{lemma}\label{normalization_helper_one}
    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
\end{lemma}
\begin{proof}
    For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
    We proceed by induction on the measure \(S\).
    That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
    \par Now, we have two cases.
    In the first case, \((e_{ij})_{ij}\) already satisfies the desired property.
    In this case we are done.
    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
    This is what we do.
    Define \(e'_{ij}\) as follows.
    \begin{itemize}
        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
        \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
    \end{itemize}
    Clearly this is a Jordan basis for \(A\).
    Further, I claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
    We have 
    \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
    \[f\left(e_{i_1, j} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}\right) = f(e_{i_1, j}) - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} f(e_{i_2, j_2 + (j - j_1)}).\]
    Clearly (by design), this expression is zero when \(j = j_1\).
    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
    Hence the measure \(S\) of this new basis is smaller, as desired.
\end{proof}

>>>>

\begin{corollary}\label{bs_iso}
    \begin{align*}
        B_{I, (\rho_i)} \cong & \prod_{k = 1}^r (\mathbb{C}^{\rho_{i_k} - 1} \times (\mathbb{C} \setminus \{0\})) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} \mathbb{C}^{\lambda_i - q_{i_0}} \times \\
        & \prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}}\mathbb{C}^{\min(p_{i_k}, \lambda_i - q_{i_k})}.
    \end{align*}
\end{corollary}
\begin{proof}
    Here we use the notation \(x \times y = (x, y)\), and so on.
    The isomorphism sends \(b \in B_{I, (\rho_i)}\) to 
    \[\prod_{k = 1}^{r}(b_{i_k1},..., b_{i_k\rho_{i_k}}) \times \prod_{i : \lambda_i \geq q_{i_0} + p_{i_1}} (b_{i1}, ..., b_{i, \lambda_i - q_{i_0}}) \times\]
    \[\prod_{k = 1}^r \prod_{\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}} (b_{i1}, ..., b_{i,\min(p_{i_k}, \lambda_i - q_{i_k})}).\]
    \cref{alternative_bs_two} says that this is an isomorphism.
\end{proof}

@@

\par We claim that there is some \(\mu(I, (\rho_i))\) such that every \((A_{0, b}, U) \in \mathcal{Q}_{I, (\rho_i)}\) is similar to \(J(\mu)\).

@@

        \par We claim that \(f_n \in W\) as well.
        To see this, consider the chain beginning with \(f_n - (A^{n + p_{i_1}} f_n \rightshift n + p_{i_1})\).

@@

\subsection{A `normalization' fact about Jordan bases}
\begin{lemma}\label{normalization_helper_one}
    For any finite-dimensional \(V\), nilpotent \(A : V \to V\), and linear \(f : V \to \mathbb{C}\), there is a Jordan basis \(e_{ij}\) for \(A\) such that there is at most one \(i\) such that there exists \(j\) such that \(f(e_{ij}) \neq 0\).
\end{lemma}
\begin{proof}
    For any Jordan basis \((e_{ij})_{ij}\) of \(A\), define
    \[S((e_{ij})_{1 \leq i \leq k, 1 \leq j \leq \lambda_i}) := \sum_i \begin{cases}-1, & \forall j. \; f (e_{ij}) = 0 \\ \lambda_i - \min\{j : f (e_{ij}) \neq 0\}, & \textrm{otherwise} \end{cases}.\]
    We proceed by induction on the measure \(S\).
    That is, let \((e_{ij})_{ij}\) be a Jordan basis for \(A\).
    Our inductive hypothesis is that if there exists a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\), then we get the desired conclusion.
    \par Now, we have two cases.
    In the first case, \((e_{ij})_{ij}\) already satisfies the desired property.
    In this case we are done.
    In the other case, there exist \(i_1, j_1, i_2, j_2\) with \(i_1 \neq i_2\), and \(f(e_{i_1j_1}) \neq 0\), and \(f(e_{i_2j_2}) \neq 0\).
    We let \(j_1, j_2\) be minimal with this property, so that \(\forall j < j_1. \; f(e_{i_1j}) = 0\), and \(\forall j < j_2. \; f(e_{i_2j}) = 0\).
    Wlog, we assume that \(\lambda_{i_1} - j_1 \leq \lambda_{i_2} - j_2\).
    \par By our inductive hypothesis, all we need to do is find a Jordan basis \((e_{ij}')_{ij}\) with \(S((e_{ij}')_{ij}) < S((e_{ij})_{ij})\).
    This is what we do.
    Define \(e'_{ij}\) as follows.
    \begin{itemize}
        \item \(e_{i_1, \lambda_1}' := e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\)
        \item For \(j < \lambda_1\), \(e_{i_1, j}' := A^{\lambda_{i_1} - j} e_{i_1, \lambda_{i_1}}'\)
        \item For \(i \neq i_1\), \(e_{ij}' := e_{ij}\).
    \end{itemize}
    Clearly this is a Jordan basis for \(A\).
    Further, we claim that \(S((e'_{ij})_{ij})  < S((e_{ij})_{ij})\).
    It suffices to show that \(\forall j \leq j_1. \; f (e_{i_1,j}) = 0\).
    We have 
    \[f (e_{i_1,j}') = f\left(A^{\lambda_{i_1} - j}\left(e_{i_1, \lambda_1} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})}e_{i_2, j_2 + (\lambda_{i_1} - j_1)}\right)\right) =\]
    \[f\left(e_{i_1, j} - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} e_{i_2, j_2 + (j - j_1)}\right) = f(e_{i_1, j}) - \frac{f(e_{i_1, j_1})}{f(e_{i_2, j_2})} f(e_{i_2, j_2 + (j - j_1)}).\]
    Clearly (by design), this expression is zero when \(j = j_1\).
    And for \(j < j_1\), we have \(f(e_{i_1, j}) = f(e_{i_2, j_2 + (j - j_1)}) = 0\), so it is zero then as well.
    Hence the measure \(S\) of this new basis is smaller, as desired.
\end{proof}
